\documentclass[../../rasd.tex]{subfiles}
\begin{document}

\section{Software System Attributes}
			
			\subsection{Reliability}
			The reliability of the system mainly depends on that of \ic{Smart Wearables} in use whose purpose is to collect \ic{User data}. It also depends on the reliability of the Internet connection when it comes to sending data to Data4Help and consequently to \ic{Third parties}.
			\subsection{Availability}
			The system must offer the maximum availability, granting its service every day at any time. The lack of service must be minimal.
				\paragraph{AutomatedSOS}
				AutomatedSOS must be active every day at any time. The lack of service is acceptable only if it is due to maintenance. AutomatedSOS \ic{Users} must have received a warning 48 hours before, and must be noticed again one hour before. \\
				Even in this case, the lack of service must be kept to a minimum.

			\subsection{Security}
			The system to be does not have particular security concerns except the ones related to privacy. The login of \ic{Users} and especially of \ic{Third parties} must be very safe (using state of the art login techniques is recommended) to avoid unauthorized individuals to access private information of \ic{Users}. Moreover, the means of communication must be encrypted to save the confidentiality of information sent to Data4Help and to \ic{Third parties}.
			
			\subsection{Portability}
			Portability of \textit{User data} from a device to another is possible by entering personal login data, also for devices with different operating systems.
			Personal data and settings are stored in a database and they are downloaded when a new device is connected.

\end{document}