\documentclass[../../rasd.tex]{subfiles}
\begin{document}

\section{Definitions, Acronyms, Abbreviations}
		\subsection{Definitions}
		\begin{description}
			\item[User:]registered individual of Data4Help who agreed on the acquisition and processing of their data (see \ic{User Data}).
			\item[User Data:]\textit{User}'s health data and location acquired by Data4Help
			\item[Third party:]a company that is willing to access \textit{User data} stored in TrackMe's database.
			\item[Service:]application available for some Data4Help \textit{Users}, generally offered by a Third party.
			\item[Group Data:]set of \textit{Users data} acquired by Data4Help. The set of \ic{Users} is determined by specific characteristics and constraints defined by the \ic{Third Party} requesting the data. When sent to the \ic{Third Party}, this data is anonymized.
			\item[Smart wearable:]smart devices that can be worn on the body as accessories. These devices are required to have specific sensors for data acquisition, to be compatible with the system to be. The adjective 'smart' refers to the possibility of connecting them to an external device, such as a smartphone, and to the ability of operating autonomously even if not connected.
			\item[Geographical area:]last position sent by a \textit{User}
			\item[Anomalous data:]health data that is outside certain intervals; these intervals identify a \textit{User} normal health condition.
			\item[User in need:]registered user of AutomatedSOS in need of assistance since their health data is \textit{amomalous}.
			\item[Run:]running competition registered on Track4Run. 
			\item[Organizer:]company or private person organizing a \textit{Run}.
			\item[Spectator:]person participating as spectator of a \textit{Run}.
			\item[Participant:]\textit{User} subscribed to Track4Run participating in a \textit{Run}.
			\item[Username:]\ic{User}'s email address.
			\item[Terms and conditions:]a set of regulations which \ic{Users} must agree to follow in order to use Data4Help and the \ic{Services} built on top of it.
			\item[Privacy statement:]describes why and how TrackMe collects and uses personal data and provides information about \ic{Users'} rights.
			
			


		\end{description}
		\subsection{Acronyms}
		\begin{description}
		\item[GPS:]Global Positioning Service
		\end{description}
		\subsection{Abbreviations}
		\begin{description}
			\item[G\subs{n}:]n\sups{th} goal
			\item[D\subs{n}:]n\sups{th} domain assumption
			\item[R\subs{n}:]n\sups{th} requirement
			\item[S\subs{n}:]n\sups{th} scenario
			\item[PR\subs{n}:]n\sups{th} performance requirement
			
		\end{description}
		
\end{document}