\documentclass[../../DD.tex]{subfiles}
\begin{document}
\section{Overview}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DATA4HELP OVERVIEW %%%%%%%%%%%%%%%%%%%%%%%%%%%%

	This diagram is a general overview of the system to be.\\
	The \ic{User} interacts with their smartphone performing several actions, including but not limited to managing their services, sending their consent, and using a service. The smartphone is constantly connected to the Data4Help Server both calling it through its REST APIs and through a Socket connection so as to send new data as soon as it is collected(\todo{SPIEGARE MEGLIO SOCKET}). The smartphone is also connected to the \ic{User's Smart wearable}, allowing for continuous data collection.\\
	The Data4Help Server is the core of the system to be. It manages all \ic{User} requests, collects its data and sends them to the database - DB Server through \todo{completare}. It also sends through a Socket connection newly collected \ic{User data} only to those \ic{Services Users} are subscribed to. It allows the forwarding of \ic{Third Party User data} requests to \ic{Users} and supports the interaction of \ic{Third Parties} with the system through their dedicated website.
	Lastly, the Third Party Service System communicates with the \ic{User's} smartphone via HTTP. \todo{SPIEGARE}


	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AUTOMATEDSOS OVERVIEW %%%%%%%%%%%%%%%%%%%%%%%%%%%%

	AutomatedSOS is based on a central server which receives \ic{User data} as soon as it is produced and constantly analyzes it. The data is sent from Data4Help to AutomatedSOS via a Socket connection always active. When AutomatedSOS recognizes a \ic{User} as a \ic{User in need}, it calls Local Emergency Services and store in the AutomatedSOS database all the relevant information, including to which Local Emergency Service the \ic{User} is being taken care of.


	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TRACK4RUN OVERVIEW %%%%%%%%%%%%%%%%%%%%%%%%%%%%

	The overview of Track4Run gives a general idea of the several components that comprise this \ic{Service}.\\
	The Track4Run Server manages all the actions that can be performed by the authors in this context. First of all, it allows \ic{Organizers} to create a \ic{Run} and manage it through a dedicated website. Moreover, it communicates with Data4Help in order to allow \ic{Users} to enroll in a \ic{Run} as \ic{Participants} and acquire their real time data while running. This data will be displayed in the dedicated \ic{Spectators} website, together with the real time position of \ic{Participants}, retrieving the real world map of the \ic{Run} through Google Maps. All data that needs to be stored, is passed to and retrieved from a database - DB Server. This data is mainly made up of \ic{Run} information.

	

	\end{document}
