\documentclass[../DD.tex]{subfiles}
\begin{document}
 \chapter{User Interface Design}
	All relevant mockups of the \ic{User} interface are included in section 3.1.1 of \hyperref[ref:3]{[3]}.
	\paragraph{Interacting with the User Application}\mbox{}\\
	\indent The following provides a description on how to move through interfaces when interacting with the User Application so as to give a clear idea of the navigation flows.
	\begin{itemize}
		\item \ic{Data4Help Welcome Page} is shown when the User Application is opened.
		\item \ic{Data4Help Welcome Page} redirects to Data4Help Login Page as soon as the User Application is loaded.
		\item \ic{Data4Help Login Page} redirects to Data4Help Sign Up Page if the \ic{User} taps on Sign Up, or redirects to Data4Help Menu if the \ic{User} fills in the form and taps on Login.
		\item \ic{Data4Help Sign Up Page}redirects to \ic{Data4Help Login Page} once the \ic{User} fills in the form and taps on Create Account (assuming inserted data is correct). If data is not correct, the interface does not change and an alert is shown.
		\item \ic{Data4Help Menu} redirects to:
			\begin{itemize}
				\item \ic{\ic{User} Services Page} if the \ic{User} taps on My Services.
				\item \ic{Services Discovery Page} if the \ic{User} taps on Discover.
				\item \ic{Data4Help Login Page} if the \ic{User} taps on Logout.				
			\end{itemize}
			My Account, My Devices, Settings, Terms and Conditions redirect to specific pages that are not listed in \hyperref[ref:3]{[3]} because they are simple and negligible interfaces. 
		\item \ic{User Services Page} redirects to \ic{User Subscribed Service Page} when the \ic{User} taps on the icon of a \ic{Service}.
			\begin{itemize}
				\item If the \ic{Service} is AutomatedSOS and the monitoring was deactivated due to a previous alarm since data was detected as \ic{Anomalous}, the interface shown is \ic{AutomatesSOSPage}.
			\end{itemize}
		\item \ic{Services Discovery Page} redirects to \ic{Add Service Page} when the \ic{User} taps on the icon of a \ic{Service}.
		\item \ic{Organizer Registration Page} is shown when an individual connects to the \ic{Organizers} dedicated website and wants to register as an \ic{Organizer}.
		\item \ic{New Run Creation Page} is shown when an \ic{Organizer} asks to create a new \ic{Run}.
		\item \ic{Runs Discovery Page} is shown when a \ic{User} taps on Track4Run in their application.
		\item \ic{Spectators Run Discovery Page} is shown when an individual connects to the \ic{Spectators} dedicated website. It redirects to \ic{Watch Real Time Run Page} when the \ic{Spectator} taps on the icon of a \ic{Run}.
	\end{itemize}
\thispagestyle{fancy}
 \end{document}
